---
title: "IP_LBB"
author: "Jeremia Widyanto"
date: "5/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# clear-up the environment
rm(list = ls())

# chunk options
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  comment = "#>"
)
```

#About Dataset
https://www.kaggle.com/datasets/jessemostipak/hotel-booking-demand?select=hotel_bookings.csv

##Context
Have you ever wondered when the best time of year to book a hotel room is? Or the optimal length of stay in order to get the best daily rate? What if you wanted to predict whether or not a hotel was likely to receive a disproportionately high number of special requests?

This hotel booking dataset can help you explore those questions!

##Content
This data set contains booking information for a city hotel and a resort hotel, and includes information such as when the booking was made, length of stay, the number of adults, children, and/or babies, and the number of available parking spaces, among other things.

All personally identifying information has been removed from the data.

##Acknowledgements
The data is originally from the article Hotel Booking Demand Datasets, written by Nuno Antonio, Ana Almeida, and Luis Nunes for Data in Brief, Volume 22, February 2019.
https://www.sciencedirect.com/science/article/pii/S2352340918315191

The data was downloaded and cleaned by Thomas Mock and Antoine Bichat for #TidyTuesday during the week of February 11th, 2020.

##Inspiration
This data set is ideal for anyone looking to practice their exploratory data analysis (EDA) or get started in building predictive models!

If you're looking for inspiration on data visualizations, check out the #TidyTuesday program, a free, weekly online event that encourages participants to create and share their code and visualizations for a given data set on Twitter.

If you'd like to dive into predictive modeling, Julia Silge has an accessible and fantastic walk-through which highlights the tidymodels R package.

#About This File
This data set contains a single file which compares various booking information between two hotels: a city hotel and a resort hotel.


#Library
```{r}
options(scipen = 99) # me-non-aktifkan scientific notation
library(tidyverse) # koleksi beberapa package R
library(dplyr) # grammar of data manipulation
library(readr) # membaca data
library(countrycode)

library(ggplot2) # plot statis
library(plotly) # plot interaktif
library(glue) # setting tooltip
library(scales) # mengatur skala pada plot
```

#Data Preparation
```{r}
hotel <- read_csv("hotel_shiny/data_input/hotel_bookings.csv")
head(hotel)
```

```{r}
glimpse(hotel)
```

#Cek unique
```{r}
length(hotel$customer_type)
length(unique(hotel$customer_type))
```

Hasil dari cek unique:
1. hotel -> factor (2) ; Hotel (H1 = Resort Hotel or H2 = City Hotel)
2. is_canceled -> factor (2) ; Value indicating if the booking was canceled (1) or not (0)
3. lead_time -> factor (479) ; Number of days that elapsed between the entering date of the booking into the PMS and the arrival date
4. arrival_date_year -> date ; Year of arrival date
5. arrival_date_month -> date ; Month of arrival date
6. arrival_date_week_number -> date ; Week number of year for arrival date
7. arrival_date_day_of_month -> date ; Day of arrival date
8. stays_in_weekend_nights ; Number of weekend nights (Saturday or Sunday) the guest stayed or booked to stay at the hotel
9. stays_in_week_nights ; Number of week nights (Monday to Friday) the guest stayed or booked to stay at the hotel
10.adults ; Number of adults
11.children ; Number of children
12.babies ; Number of babies
13.meal -> factor (5); Type of meal booked. Categories are presented in standard hospitality meal packages: Undefined/SC – no meal package; BB – Bed & Breakfast; HB – Half board (breakfast and one other meal – usually dinner); FB – Full board (breakfast, lunch and dinner)
14.country -> factor (178) ; Country of origin. Categories are represented in the ISO 3155–3:2013 format
15.market_segment -> factor (8) ; Market segment designation. In categories, the term “TA” means “Travel Agents” and “TO” means “Tour Operators”
16.distribution_channel -> factor (5) ; Booking distribution channel. The term “TA” means “Travel Agents” and “TO” means “Tour Operators”
17.is_repeated_guest -> factor (2) ; Value indicating if the booking name was from a repeated guest (1) or not (0)
18.previous_cancellations ; Number of previous bookings that were cancelled by the customer prior to the current booking
19.previous_bookings_not_canceled ; Number of previous bookings not cancelled by the customer prior to the current booking
20.reserved_room_type -> factor (10) ; Code of room type reserved. Code is presented instead of designation for anonymity reasons.
21.assigned_room_type -> factor (12) ; Code for the type of room assigned to the booking. Sometimes the assigned room type differs from the reserved room type due to hotel operation reasons (e.g. overbooking) or by customer request. Code is presented instead of designation for anonymity reasons.
22.booking_changes ; Number of changes/amendments made to the booking from the moment the booking was entered on the PMS until the moment of check-in or cancellation
23.deposit_type -> factor (3) ; Indication on if the customer made a deposit to guarantee the booking. This variable can assume three categories: No Deposit – no deposit was made; Non Refund – a deposit was made in the value of the total stay cost; Refundable – a deposit was made with a value under the total cost of stay.
24.agent -> factor (334) ; ID of the travel agency that made the booking
25.company -> factor (353) ; ID of the company/entity that made the booking or responsible for paying the booking. ID is presented instead of designation for anonymity reasons
26.days_in_waiting_list ; Number of days the booking was in the waiting list before it was confirmed to the customer
27.customer_type -> factor (4) ; Type of booking, assuming one of four categories: Contract - when the booking has an allotment or other type of contract associated to it; Group – when the booking is associated to a group; Transient – when the booking is not part of a group or contract, and is not associated to other transient booking; Transient-party – when the booking is transient, but is associated to at least other transient booking
28.adr ; Average Daily Rate as defined by dividing the sum of all lodging transactions by the total number of staying nights
29.required_car_parking_spaces ; Number of car parking spaces required by the customer
30.total_of_special_requests ; Number of special requests made by the customer (e.g. twin bed or high floor)
31.reservation_status -> factor (3) ; Reservation last status, assuming one of three categories: Canceled – booking was canceled by the customer; Check-Out – customer has checked in but already departed; No-Show – customer did not check-in and did inform the hotel of the reason why
32.reservation_status_date; Date at which the last status was set. This variable can be used in conjunction with the ReservationStatus to understand when was the booking canceled or when did the customer checked-out of the hotel

#Ubah tipe data
```{r}
a <- countrycode(sourcevar = hotel$country, origin = "iso3c", destination = "country.name")

#dplyr
hotel_clean <- hotel %>% 
  mutate(
    hotel = as.factor(hotel),
    is_canceled = as.factor(is_canceled),
    meal = as.factor(meal),
    country = as.factor(country),
    market_segment = as.factor(market_segment),
    distribution_channel = as.factor(distribution_channel),
    is_repeated_guest = as.factor(is_repeated_guest),
    reserved_room_type = as.factor(reserved_room_type),
    assigned_room_type = as.factor(assigned_room_type),
    deposit_type = as.factor(deposit_type),
    agent = as.factor(agent),
    company = as.factor(company),
    customer_type = as.factor(customer_type),
    reservation_status = as.factor(reservation_status)
    ) %>% 
  mutate(
    country_name = countrycode("country", origin = "iso3c", destination = "country.name")
  )

# preparation
hotel_count <- hotel_clean %>% 
  group_by(country) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

# penambahan tooltip
hotel_count <- hotel_count %>% 
  mutate(label = glue("Country: {country}
                      Count: {count} hotels"))

# ggplot
plot1 <- hotel_count %>% 
  ggplot(aes(x = count, 
             y = reorder(category_id, count),
             fill = count,
             text = label)) +
  geom_col() +
  scale_fill_gradient(low = "red", high = "black") +
  theme_minimal() +
  theme(legend.position = "none") + 
  labs(title = NULL,
       x = "Video Count",
       y = NULL)

# plotly
ggplotly(plot1, tooltip = "text")
```







